---
title: "Long footnote, code"
author: "Bryan Shalloway"
date: "6/7/2019"
output: 
  html_document:
  github_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Ch. 20

* `str` checks structure (excellent for use with lists)
* `attr` and `attributes` get and set attributes
  + main types of attributes: **Names**, **Dimensions/dims**, **Class**. Class is important for object oriented programming which is covered in more detail here: http://adv-r.had.co.nz/OO-essentials.html#s3 
* Used together to investigate details of code for functions
    * `useMethod` in function syntax indicates it is a generic function
    * `methods` lists all methods within a generic
    * `getS3method` to show specific implementation of a method
```{r}
as.Date
methods("as.Date")
getS3method("as.Date", "default")
```

* Some tidyverse functions are not always easy to unpack with just the above[^tidyfuns]
* **Augmented vectors**: vectors with additional attributes, e.g. factors (levels, class = factors), dates and datetimes (tzone, class = (POSIXct, POSIXt)), POSIXlt (names, class = (POSIXLt, POSIXt)), tibbles (names, class = (tbl_df, tbl, data.frame), row.names) -- in the integer, double and double, list, list types.
  * data frames only have class `data.frame`, whereas tibbles have `tbl_df`, and `tbl` as well
* `class` get or set class attribute
* `unclass` returns copy with 'class' attribute removed

[^tidyfuns]: For example:  
    ```{r}
    select
    methods("select")
    getS3method("select", "data.frame")
    dplyr:::select_impl
    ```  
    * These details may not illuminate for you how `select()` works  
    * Note that R has multiple systems for object oriented programming -- these topics are covered in [Advanced R Progamming](https://adv-r.hadley.nz/)  
    
